---
title: "Reproducible Research project week2"
author: "Koji"
date: "2021/11/5"
output: html_document
---

download zip file and unzip them
```{r}
library(ggplot2)
library(lubridate)
library(dplyr)
Sys.setenv("LANGUAGE"="e")
path <- getwd()
url <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
download.file(url, file.path(path, "Activity_monitoring_data.zip"))
unzip(zipfile = "Activity_monitoring_data.zip")
```
read activity data and create sum data to sum_step
```{r}
activity <- read.csv("activity.csv")
sum_step <- aggregate(steps ~ date, data = activity, sum, na.rm = TRUE)
```
make histogram 
```{r}
hst <- qplot(steps, data = sum_step, main = "Total Number of Steps taken each day", bins = 10)
hst
```
Calculate Mean and Median number of step taken each day
```{r}
mean(sum_step$steps, na.rm = TRUE)
median(sum_step$steps, na.rm = TRUE)
```
Time series plot of the average number of steps taken
```{r}
time_order <- aggregate(steps ~ interval, data = activity, mean, na.rm = TRUE)
qplot(interval,steps, data = time_order, main = "Time series plot of the average number of steps taken", xlab = "Interval", geom = "line")
head(time_order)
```

The 5-minute interval that, on average, contains the maximum number of steps
```{r}
time_order$interval[max(time_order$steps)]
time_order$interval[is.na(time_order$steps)]
```
# Imputing mising values
1.Calculate and report the total number of missing values in the dataset
```{r}
nrow(is.na(activity))
```

2.Devise a strategy for filling in all of the missing values in the dataset.
replace NA value in steps into mean corresponding to same interval
```{r}
#time_order contains only one row per day but activity has multiple rows
#[activity$interval$interval] could be 0 and cause error!!
#So exclude activity$interval = 0 and treat it separately
for (i in 1:length(activity$steps)) {if(is.na(activity$steps[i])) {
        if (activity$interval[i] != 0){
    activity$steps[i] <- time_order$steps[time_order$interval == activity$interval[i]]
        }
        else {activity$steps[i] <- time_order$steps[1]}
}
}
head(activity, 20)
```
3.Create a new dataset that is equal to the original dataset but with the missing data filled in.
```{r}
new_data <- activity
```

4.Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day
```{r}
new_hist <- aggregate(steps ~ date, data = new_data, sum)
qplot(steps, data = new_hist, bins = 10)

# calculate mean and mediuam
mean(new_hist$steps)
median(new_hist$steps)
```
#Are there differences in activity patterns between weekdays and weekends?
1.Create a new factor variable in the dataset with two levels – “weekday” and “weekend” indicating whether a given date is a weekday or weekend day.

```{r}
new_data$date <- ymd(new_data$date)
new_data <- mutate(new_data, daytype = weekdays(new_data$date))
head(new_data, 20)

```

2.Make a panel plot containing a time series plot (i.e.type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis). See the README file in the GitHub repository to see an example of what this plot should look like using simulated data.

